Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-10 ms/main.tex
Add mean fitness graph

%%% Figure: invasion
\begin{figure}[b]
  \centering
   \includegraphics[scale=0.5]{Frequency_of_invadors.eps}
  \caption{
  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable coexistence of cooperators and defactors with soical association $\alpha_1$. 
  The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
  The blue curve describes the frequency of the invadors, starting from initial frequency of 1\%.
  The orange curve describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency which is described by the black dashed line. 
  The frequency of cooperators after the fixation of the invadors is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.
  In this case $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
  }
  \label{fig:invasion}
\end{figure}

>>>>

%%% Figure: invasion
\begin{figure}[b]
  \centering
   \includegraphics[scale=0.5]{Frequency_of_invadors.eps}~
   \includegraphics[scale=0.5]{mean_fitness_of_invadors.eps}
  \caption{
  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable coexistence of cooperators and defactors with soical association $\alpha_1$. 
  The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
  \textbf{(a)} The blue curve describes the frequency of the invadors, starting from initial frequency of 1\%.
  The orange curve describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency which is described by the black dashed line. 
  The frequency of cooperators after the fixation of the invadors is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.\\
  \textbf{(b)} describes the mean fitness as a function of time (generations). 
  As the frequency of the invadors increases the mean fitness decreases. \\
  In both panels $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
  }
  \label{fig:invasion}
\end{figure}
%TDODO: revisit this caption
